Improving Dynamic Kidney Exchange

### 2018-02-08 paper.tex
New tables

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,pdflscape,subfigure,array,hyperref}
\usepackage{cite}
\usepackage{natbib}
\usepackage{etoolbox}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage[font=footnotesize]{caption}

@@

%\doublespacing

@@

\begin{table}[H]
\centering
\begin{tabular}{lr}
\toprule
Pair blood type &         Probability \\
\midrule
(O, O) &  0.058689 \\
(O, A) &  0.373803 \\
(O, B) &  0.158257 \\
(O, AB) &  0.042669 \\
(A, O) &  0.041119 \\
(A, A) &  0.028809 \\
(A, B) &  0.110888 \\
(A, AB) &  0.029899 \\
(B, O) &  0.017410 \\
(B, A) &  0.110888 \\
(B, B) &  0.005160 \\
(B, AB) &  0.012660 \\
(AB, O) &  0.004690 \\
(AB, A) &  0.003290 \\
(AB, B) &  0.001390 \\
(AB, AB) &  0.000380 \\
\bottomrule
\end{tabular}
\caption{Blood type probabilities in the ABO environment}
\label{tab:abo_blood_type}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=1textwidth]{/Users/vitorhadad/Documents/kidney/matching/figures/computed_cpra.pdf}.
\caption{Computed patient and donor cPRA.}
\label{fig:cpra}
\end{figure}

@@

Figure \ref{}

 \begin{figure}
 \centering
 \hspace*{-4cm}
 \includegraphics[width=1.5\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/greedy_opt_comparison_mcl2.pdf}
 \caption{\texttt{Myopic} matches roughly the same number of pairs per period as \texttt{OPT} when the death rate is high (moving rightwards on the graphs), or when entry rate is high (moving downwards on the graphs).}
 \label{fig:mab}
 \end{figure}

\subsection{Algorithms}

We divide our algorithms into three classes: \emph{direct prediction} methods, \emph{multi-armed bandit} methods and \emph{reinforcement learning} methods. They are explained next.

@@

Dynamic and static algorithms can split their work: the former can determine which pairs should be matched at each period, while the latter decides how they should be matched among themselves. The \emph{direct prediction} exploits this insight, essentially reducing the problem to a classification task: at each period, they aim to produce a 0-1 label for each node indicating whether is should be matched in this period (1) or left for later (0). Selected nodes are then passed to a static solver that finds the maximal matching among them. Once these nodes are cleared, time evolves to the next period. This is illustrated in Figure \ref{fig:direct_prediction}.

\begin{figure}
\centering
\hspace*{-1cm}
\includegraphics[width=1.1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/direct_prediction.pdf}.
\caption{Direct prediction methods.}
\label{fig:direct_prediction}
\end{figure}

In order to produce data to feed into our ``classifier", each environment was simulated and solved using OPT, with each pair's observable characteristics as regressors, and a binary variable indicating whether they were matched or not. Each resulting artifical dataset of approximately 2 million observations was then fed to a series of predictive algorithms, including penalized logistic regression\cite{wu2009genome}, support vector machines with radial basis function kernels\cite{cortes1995support}, random forest classifiers\cite{breiman2001random}, gradient tree boosting classifiers\cite{friedman2001greedy} and deep feedforward networks\cite{goodfellow2016deep}. The performance of these algorithms as classification methods is compared in Table \ref{tab:direct_prediction}.

@@

Let $c^{*}$ be a cycle that maximizes expected pseudo-rewards during one round of the algorithm:
$$c^{*} \in \arg\max_{c} E[r_{c\ell}] $$

 A \emph{multi-armed bandit} algorithm is a procedure to minimize \emph{regret}

@@

 \begin{figure}
 \centering
 \includegraphics[width=1.1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/mab_step.pdf}
 \caption{Pseudo-reward computation in one step of a multi-armed bandit algorithm.}
 \label{fig:mab_step}
 \end{figure}

% \subsection{Methods}
% 
% In this work, we propose a new kidney exchange algorithm that combines simulation-based search with a policy parametrized by neural networks. In the next paragraphs, we will explain each of these components in detail. However, first let us provide some motivation.
% 
% We begin by noting that we have a promising setup, as we are in possession of: good estimates of the data-generating process for each environment; an algorithm that is able to compute optimal actions, even if only in hindsight (\texttt{OPT}); one clear benchmark that we must beat (\texttt{Myopic}). At first glance, then, one might hypothesize that it would be possible to find reasonably good solutions using only simulations: simply simulate future states to a long horizon ahead, and choose today the action that on average leads to higher future rewards -- or the one that is most often chosen by \texttt{OPT}, or the one that most frequently leads to beating \texttt{Myopic}. Unfortunately, this turns out to be overly optimistic: approaches solely based on simulations do not perform very well, as shown in Table \ref{simulations_only}. We believe that the reason for this poor performance is the high branching factor of the problem -- in other words, there is high uncertainty about what the next period will look like.
% 
% 
% Reducing the problem:
% 
% 1. Our "actions" are simply a number of binary flags indicating who should be matched today and who should not
% 2. We can leverage the optimal algorithm to reduce the MDP to a simpler period-by-period MAB problem
% 3. Use 
% 
% % In lieu of just simulations, we propose to see each period's problem as a Bayesian multi-armed bandit problem (MAB). ... estimate... then use estimates as pseudo-counts... then sample from posterior.
% 
%

%\insert{algo1.tex}

% Using Thompson sampling at each episode might sound like a greedy approach to a problem where current actions might have effects on future rewards, but here we *are* using future rewards since we can simulate the future \emph{and} also assume that we will be act optimally within a time horizon.

@@

\subsection{Short-run gains}

@@

\bibliographystyle{/Users/vitorhadad/Documents/kidney/matching/paper/te.bst}
\bibliography{references}

@@

>>>>

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,caption,color,setspace,sectsty,comment,footmisc,pdflscape,subfigure,array,hyperref}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{natbib}
\usepackage{etoolbox}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage[font=footnotesize]{caption}

@@

\doublespacing

@@

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/computed_cpra.pdf}
\caption{Computed patient and donor cPRA.}
\label{fig:cpra}
\end{figure}

@@

Our benchmark

 \begin{figure}[H]
 \centering
 \hspace*{-4cm}
 \includegraphics[width=1.5\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/greedy_opt_comparison_mcl2.pdf}
 \caption{\texttt{Myopic} matches roughly the same number of pairs per period as \texttt{OPT} when the death rate is high (moving rightwards on the graphs), or when entry rate is high (moving downwards on the graphs).}
 \label{fig:greedy_opt_comparison_mcl2}
 \end{figure}

\subsection{Methods}

We divide our algorithms into three classes: \emph{direct prediction} methods, \emph{multi-armed bandit} methods. As we will explain shortly,

@@

Dynamic and static algorithms can split their work: the former can determine which pairs should be matched at each period, while the latter decides how they should be matched among themselves. The \emph{direct prediction} exploits this insight, essentially reducing the problem to a classification task: at each period, we aim to produce a 0-1 label for each node indicating whether is should be matched in this period (1) or left for later (0). Selected nodes are then passed to a static solver that finds the maximal matching among them. Once these nodes are cleared, time evolves to the next period. This is illustrated in Figure \ref{fig:direct_prediction}.

\begin{figure}[H]
\centering
\hspace*{-1cm}
\includegraphics[width=1.1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/direct_prediction.pdf}.
\caption{Direct prediction methods.}
\label{fig:direct_prediction}
\end{figure}

In order to produce data to feed into our ``classifier", we simulated and solved a 1000-period run environment was simulated and solved using OPT using with each each node's observable characteristics as regressors, and a binary variable indicating whether they were matched or not as the regressand. The resulting artificial dataset of approximately 2 million observations was then fed to a series of predictive algorithms, including penalized logistic regression\citep{wu2009genome}, support vector machines with radial basis function kernels\citep{cortes1995support}, random forest classifiers\citep{breiman2001random}, gradient tree boosting classifiers\citep{friedman2001greedy} and deep feedforward networks\citep{goodfellow2016deep}. The performance of these algorithms as classification methods is compared in Table \ref{tab:direct_prediction}.

@@

Let $c^{*}$ be a cycle that maximizes expected pseudo-rewards during one round of the algorithm:
$$c_{\ell}^{*} \in \arg\max_{c} E[r_{c,\ell}] $$

 Also, let \emph{regret} be defined as the difference between expected reward of the optimal choice $c^*$ and its own selected choice $c_{\ell}$.

 $$\Delta_\ell := E[r_{c^{*},\ell}] - E[r_{c,\ell}]$$

 A \emph{multi-armed bandit} (MAB) algorithm is a procedure to minimize the cumulative regret over $L$ rounds. A good MAB algorithm will act so as to balance exploration (trying out different choices to get high-quality estimates of their rewards) and exploitation (using out better choices more often to increase total rewards).

 The literature on bandit algorithms is extensive and spans at least seventy years of research \citep{lattimore2018bandits}. Here we will focus on binary

@@

 \begin{figure}
 \centering
 \includegraphics[width=1.1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/mab_step.pdf}
 \caption{Pseudo-reward computation that takes place during one round of a multi-armed bandit algorithm.}
 \label{fig:mab_step}
 \end{figure}

@@

\subsection{Direct method}

@@

\bibliographystyle{te.bst}
\bibliography{references}

@@

\begin{table}[H]
\centering
\singlespacing
\begin{tabular}{lr}
\toprule
Pair blood type &         Probability \\
\midrule
(O, O) &  0.058689 \\
(O, A) &  0.373803 \\
(O, B) &  0.158257 \\
(O, AB) &  0.042669 \\
(A, O) &  0.041119 \\
(A, A) &  0.028809 \\
(A, B) &  0.110888 \\
(A, AB) &  0.029899 \\
(B, O) &  0.017410 \\
(B, A) &  0.110888 \\
(B, B) &  0.005160 \\
(B, AB) &  0.012660 \\
(AB, O) &  0.004690 \\
(AB, A) &  0.003290 \\
(AB, B) &  0.001390 \\
(AB, AB) &  0.000380 \\
\bottomrule
\end{tabular}
\caption{Blood type probabilities in the ABO environment}
\label{tab:abo_blood_type}
\end{table}

\begin{table}
  \centering
  \singlespacing
  \hspace*{-3cm}
  \input{tables/traditional_ml.tex}
  \caption{\textbf{Traditional methods} \\ Performance of traditional econometric and classification methods when predicting whether a node will be matched (1) or not (0).
  Recall is true positive rate $\frac{tp}{tp+fn}$;
  Specificity is true negative rate $\frac{tp}{tn+fp}$;
  Precision is $\frac{tp}{tp+fp}$; Accuracy is $\frac{tp+tn}{tp+tn+fp+fn}$. See section \ref{sec:???} for methodology and section \ref{sec:??} for discussion of results.
  }
  \label{tab:tradional_ml}
\end{table}
